---
title: "DataSience_FinalProject"
author: "Jan Steinwender & Paul Pavlis"
date: "2020-10-28"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Clean the environment variables (*Temporary*)
*Remove this whole header before handing the project in. This is just so that working with the document is easier*
```{r}
rm(list = ls())
```

# Load needed libraries

```{r}
library(tidyverse)
library(ggplot2)
```
# Data wrangling

## Data import from csv file

```{r}
restaurant_data = read.csv(file = "restaurants_data.csv")
restaurant_data = restaurant_data %>% na_if("") # Set empty data entries to NA
```

## Clean the data

### Rename and remove columns

```{r}
restaurant_data = as_tibble(restaurant_data)

restaurant_data = restaurant_data %>%
  rename("Cuisine_Style" = Cuisine.Style) %>%
  rename("Price_Range" = Price.Range) %>%
  rename("Review_Number" = Number.of.Reviews)

restaurant_data = restaurant_data %>%
  mutate(X = NULL, URL_TA = NULL, ID_TA = NULL) # Remove useless lines
```

### Correct the column types

```{r}
restaurant_data = restaurant_data %>% mutate(City = as_factor(City)) # Change from character to factor

restaurant_data = restaurant_data %>% mutate(Price_Range = as_factor(Price_Range)) # Change from character to factor
restaurant_data = restaurant_data %>% mutate(Price_Range = fct_recode(
  Price_Range,
  "low" = "$",
  "medium" = "$$ - $$$",
  "high" = "$$$$"
)) # Rename the levels

```

### Check duplicated and NULL values

```{r}
duplicated(restaurant_data) %>% sum()
restaurant_data = restaurant_data %>% distinct() # Remove duplicates


is.na(restaurant_data) %>% sum()
sapply(restaurant_data, function(x) sum(is.na(x)))
```

## Summary

```{r}
restaurant_data
str(restaurant_data)
summary(restaurant_data)
```

# Visualisation

## ...

Beispiele zum testen ob es eh funktioniert:
```{r}
ggplot(restaurant_data, aes(x = Price_Range)) + geom_bar()
ggplot(restaurant_data, aes(x = Review_Number, y = Ranking)) + geom_point(aes(col = Rating))
```
